Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-01-04 Master Thesis/synopsis.tex
Add back missing Lemma

\iffalse
\begin{lemma}\phantomsection\label{2.3}
\begin{enumerate}[(i)]
\item $\operatorname{Spv}(K)$, together with the maps $\pi_{\mathfrak{X}}$, is the projective limit of topological spaces: 
\[\operatorname{Spv}(K) =\varprojlim_{\mathfrak{X}\in\mathfrak{M}(K)}\mathfrak{X}\]
In particular we have:
\[ |\operatorname{Spv}(K)| =\varprojlim_{\mathfrak{X}\in\mathfrak{M}(K)}|\mathfrak{X}| \]
\item For all $v\in\operatorname{Spv}(K)$ we have:
\[ \mathcal{O}_v = \varinjlim_{\mathfrak{X}\in\mathfrak{M}(K)}\mathcal{O}_{\mathfrak{X},\pi_\mathfrak{X}(v)} \]
\item For $v\in\operatorname{Spv}(K)$ let $K_v$ be the quotient field of a henselization of $\mathcal{O}_v$ and for $\mathfrak{X}\in\mathfrak{M}(K),\ x\in\mathfrak{X}$ let $K_\mathfrak{X}$ be the quotient field of a henselization of $\mathcal{O}_{\mathfrak{X},x}$. Then:
\[ K_v=\varinjlim_{\mathfrak{X}\in\mathfrak{M}(K)}K_{\pi_\mathfrak{X}(v)} \]
\end{enumerate}
\end{lemma}
\fi

@@

\begin{proof}
Observe $\varphi(-1)^2 = \varphi(1) = 1$, and since $\varphi$ is bijective on $K'^\times$, it follows $\varphi(-1) \neq 1$ and hence $\varphi(-1) = -1$. Now, to prove the assertion, it suffices to show $\varphi(x + y) = \varphi(x) + \varphi(y)$ for all $x,y\in K'^\times$.
\begin{itemize}
\item \textit{Case 1:} If $x + y = 0$, we have:
\[ \varphi(x + y) = 0 = \varphi(x) + \varphi(-1)\varphi(x) = \varphi(x) + \varphi(-x) = \varphi(x) + \varphi(y) \]
\item \textit{Case 2:} Let $x + y\neq 0$ and $S\subset X_0$ be a finite subset such that $\varphi(x + y)$, $\varphi(x)$ and $\varphi(y)$ are contained in $K^S$. Looking at the commutative diagram in \mbox{Step 1} we get
\begin{align*}
r_P(\varphi(x+ y)) &= \varphi_P(r_{P'}(x + y)) \\
&= \varphi_P(r_{P'}(x)) + \varphi_P(r_{P'}(y)) = r_P(\varphi(x) + \varphi(y))
\end{align*}
for all $P\in X_0\setminus S$. Note that $\varphi_P: k(P')\to k(P)$ is a field isomorphism and that the residue maps $r_{P}: \mathcal{O}_{P} \to k(P)$ are ring homomorphisms. Since $K^S\to \prod_{P\in X_0\setminus S} k(P)^\ast$ is injective, we get $\varphi(x+y) = \varphi(x) + \varphi(y)$.\qedhere
\end{itemize}
\end{proof}

>>>>

\begin{lemma}\phantomsection\label{2.3}
\begin{enumerate}[(i)]
\item $\operatorname{Spv}(K)$, together with the maps $\pi_{\mathfrak{X}}$, is the projective limit of topological spaces: 
\[\operatorname{Spv}(K) =\varprojlim_{\mathfrak{X}\in\mathfrak{M}(K)}\mathfrak{X}\]
In particular we have:
\[ |\operatorname{Spv}(K)| =\varprojlim_{\mathfrak{X}\in\mathfrak{M}(K)}|\mathfrak{X}| \]
\item For all $v\in\operatorname{Spv}(K)$ we have:
\[ \mathcal{O}_v = \varinjlim_{\mathfrak{X}\in\mathfrak{M}(K)}\mathcal{O}_{\mathfrak{X},\pi_\mathfrak{X}(v)} \]
\item For $v\in\operatorname{Spv}(K)$ let $K_v$ be the quotient field of a henselization of $\mathcal{O}_v$ and for $\mathfrak{X}\in\mathfrak{M}(K),\ x\in\mathfrak{X}$ let $K_x$ be the quotient field of a henselization of $\mathcal{O}_{\mathfrak{X},x}$. Then:
\[ K_v=\varinjlim_{\mathfrak{X}\in\mathfrak{M}(K)}K_{\pi_\mathfrak{X}(v)} \]
\end{enumerate}
\end{lemma}

\begin{proof}
(i) and (ii) follow from [HK], Lemma 2.4.3 and (iii) is a consequence of (ii) and [EGA IV] 18.6.14.
\end{proof}

@@

\begin{proof}
Observe that $\varphi(-1)^2 = \varphi(1) = 1$, and since $\varphi$ is bijective on $K'^\times$, it follows $\varphi(-1) \neq 1$ and hence $\varphi(-1) = -1$. Now, to prove the assertion, it suffices to show $\varphi(x + y) = \varphi(x) + \varphi(y)$ for all $x,y\in K'^\times$.
\begin{itemize}
\item \textit{Case 1:} If $x + y = 0$, we have:
\[ \varphi(x + y) = 0 = \varphi(x) + \varphi(-1)\varphi(x) = \varphi(x) + \varphi(-x) = \varphi(x) + \varphi(y) \]
\item \textit{Case 2:} Let $x + y\neq 0$ and $S\subset X_0$ be a finite subset such that $\varphi(x + y)$, $\varphi(x)$ and $\varphi(y)$ are contained in $K^S$. Looking at the commutative diagram in \mbox{Step 1} we get
\begin{align*}
r_P(\varphi(x+ y)) &= \varphi_P(r_{P'}(x + y)) \\
&= \varphi_P(r_{P'}(x)) + \varphi_P(r_{P'}(y)) = r_P(\varphi(x) + \varphi(y))
\end{align*}
for all $P\in X_0\setminus S$. Note that $\varphi_P: k(P')\to k(P)$ is a field isomorphism and that the residue maps $r_{P}: \mathcal{O}_{P} \to k(P)$ are ring homomorphisms. Since $K^S\to \prod_{P\in X_0\setminus S} k(P)^\ast$ is injective, we get $\varphi(x+y) = \varphi(x) + \varphi(y)$.\qedhere
\end{itemize}
\end{proof}
